A Deterministic and Terminating Semantics for the Synchronous Programming Language~\CEU

### 2018-02-18 03-semantics.tex
Corrige regra loop-adv na Seção 3.2
Adiciona as macros \outpush e \outpop à header.tex
Essas macros corrigem a tipografia de \out[push] e \out[pop].

A complete reaction consists of the following series of transitions:
\begin{align*}
  \<p,0,e_\ext>\out[push]\<p_1,1,\nil>
  \Big[\null\nst[*]\null\out\null\Big]\!\!\ast
  \null\nst[*]\null\out[pop]\<p',0,\nil>\,.
\end{align*}
%
%-
% \begin{align*}
% a) &\5\5
%     \LL p,0,ext \RR
%         \1\xrightarrow[out]{push}\1
%     \LL q,1,\epsilon \RR
% \\
% b) &\5\5 \1[ \1\xrightarrow[in]{*}\1
%     \LL r,i,e \RR
%         \1\xrightarrow[out]\1
%     \LL s,j,\epsilon \RR \1]*
% \\
% c) &\5\5 \1\xrightarrow[in]{*}\1
%     \LL t,k,\epsilon \RR
%         \1\xrightarrow[out]{pop}\1
%     \LL u,0,\epsilon \RR
% \end{align*}
%-
%
First, a~$\out[push]$ starts a nested reaction at level~1.
Then, a series of alternations between zero or more~$\nst$ transitions (nested reactions) and a
single~$\out$ transition (stack operation) takes place.
Finally, a last~$\out[pop]$ transition decrements the
stack level to~0 and terminates the reaction.

@@

The rules for loops are analogous to sequences, but use ``\code{@}'' as
separators to properly bind breaks to their enclosing loops:
\begin{align*}
  \<\ceu{\Loop{p}},n,\nil>
  &\nst\<\ceu{p\AtLoop{p}},n,\nil>\Rtag{loop-expd}\\[2\jot]
  %%
  &\hskip-6.35em
  \AxiomC{$\<p,n,\nil>\nst\<p',n,e>$}
  \UnaryInfC{$\<\ceu{p\AtLoop{p}},n,\nil>\nst\<\ceu{p'\AtLoop{p}},n,e>$}
  \DisplayProof
  \Rtag{loop-adv}\\[2\jot]
  %%
  \<\ceu{\Nop\AtLoop{p}},n,\nil>
  &\nst\<\ceu{\Loop{p}},n,\nil>\Rtag{loop-nop}\\[2\jot]
  %%
  \<\ceu{\Break\AtLoop{p}},n,\nil>
  &\nst\<\ceu{\Nop},n,\nil>\Rtag{loop-brk}
\end{align*}

>>>>

A complete reaction consists of the following series of transitions:
\begin{align*}
  \<p,0,e_\ext>\outpush\<p_1,1,\nil>
  \Big[\null\nst[*]\null\out\null\Big]\!\!\ast
  \null\nst[*]\null\outpop\<p',0,\nil>\,.
\end{align*}
%
%-
% \begin{align*}
% a) &\5\5
%     \LL p,0,ext \RR
%         \1\xrightarrow[out]{push}\1
%     \LL q,1,\epsilon \RR
% \\
% b) &\5\5 \1[ \1\xrightarrow[in]{*}\1
%     \LL r,i,e \RR
%         \1\xrightarrow[out]\1
%     \LL s,j,\epsilon \RR \1]*
% \\
% c) &\5\5 \1\xrightarrow[in]{*}\1
%     \LL t,k,\epsilon \RR
%         \1\xrightarrow[out]{pop}\1
%     \LL u,0,\epsilon \RR
% \end{align*}
%-
%
First, a~$\outpush$ starts a nested reaction at level~1.
Then, a series of alternations between zero or more~$\nst$ transitions (nested reactions) and a
single~$\out$ transition (stack operation) takes place.
Finally, a last~$\outpop$ transition decrements the
stack level to~0 and terminates the reaction.

@@

The rules for loops are analogous to sequences, but use ``\code{@}'' as
separators to properly bind breaks to their enclosing loops:
\begin{align*}
  \<\ceu{\Loop{p}},n,\nil>
  &\nst\<\ceu{p\AtLoop{p}},n,\nil>\Rtag{loop-expd}\\[2\jot]
  %%
  &\hskip-6.35em
  \AxiomC{$\<q,n,\nil>\nst\<q',n,e>$}
  \UnaryInfC{$\<\ceu{q\AtLoop{p}},n,\nil>\nst\<\ceu{q'\AtLoop{p}},n,e>$}
  \DisplayProof
  \Rtag{loop-adv}\\[2\jot]
  %%
  \<\ceu{\Nop\AtLoop{p}},n,\nil>
  &\nst\<\ceu{\Loop{p}},n,\nil>\Rtag{loop-nop}\\[2\jot]
  %%
  \<\ceu{\Break\AtLoop{p}},n,\nil>
  &\nst\<\ceu{\Nop},n,\nil>\Rtag{loop-brk}
\end{align*}
